Supporting ecological decision making using feature-selection and variable importance

### 2020-02-09 docs/00-manuscripts/ieee/performance-best-per-learner.tex
move paper to docs/manuscript

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & XGBoost & Borda & 30.56 & 13.37 \\ 
  2 & HR & RF & MRMR & 31.44 & 15.08 \\ 
  3 & HR-NRI-VI & SVM & Relief & 31.58 & 15.60 \\ 
  4 & NRI & Ridge-CV & No Filter & 33.23 & 8.22 \\ 
  5 & HR & Lasso-CV & No Filter & 47.22 & 20.52 \\ 
  6 & HR & Lasso-MBO & No Filter & 55.11 & 22.84 \\ 
  7 & HR & Ridge-MBO & No Filter & 55.11 & 22.84 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & RF & Relief & 30.66 & 13.57 \\ 
  2 & HR & XGBoost & Borda & 30.75 & 13.75 \\ 
  3 & HR-NRI & SVM & Borda & 31.70 & 15.62 \\ 
  4 & NRI & Ridge-CV & No Filter & 33.31 & 8.17 \\ 
  5 & HR & Lasso-CV & No Filter & 47.22 & 20.52 \\ 
  6 & HR & Lasso-MBO & No Filter & 55.11 & 22.84 \\ 
  7 & HR & Ridge-MBO & No Filter & 55.11 & 22.84 \\ 
   \hline
\end{tabular}
}
\end{table}

### 2020-02-09 docs/00-manuscripts/journal/manuscript.tex
move paper to docs/manuscript

@@

\noindent Filter method "information gain" is by creation only defined for class responses:

@@

where $H$ is the conditional entropy of the response variable (class) or the feature (attribute), respectively.
To be able to use this method with a numeric response, the variable is discretized into equal bins and treated as a class variable.
While the number of bins can be treated as a hyperparameter of the filter method, the default of the R package implementation of \texttt{$n_{bin}$ = 5} was used after rank correlations of > 0.9 for different bin sizes have been explored.
% TODO: Add reference to appendix, put plot into appendix

>>>>

\begin{figure} [t!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[width=0.5\textwidth] {defol-grid-3000px.jpg}}
        \caption{Example trees showing different levels of defoliation as interpreted by the surveyor: 10 \% (top-left), 20 \% (top-right), 40 \% (bottom-left), 60-70 \% (bottom-right).}
		\label{fig:defol-trees}
	\end{center}
\end{figure}

@@

\noindent Filter method "information gain" is only defined for nominal response variables:

@@

where $H$ is the conditional entropy of the response variable (class) or the feature (attribute), respectively.
To be able to use this method with a numeric response, the variable is discretized into equal bins and treated as a class variable.
While the number of bins can be treated as a hyperparameter of the filter method, we decided to use \texttt{$n_{bin}$ = 10} after rank correlations of > 0.9 for different bin sizes were observed in a side analysis.
